Simulating an Isolated Dwarf Galaxy with Energetic Feedback and Chemical Yields from Individual Stars

### 2018-04-19 main.tex
Update on Overleaf.

\begin{abstract}
%\textbf{CHANGE: Cleaned up a few sentences. better intro + last sentence. added wind caveat. removed large H2 content mention (should I put this last one back?).}
%Galactic chemical evolution is driven through stellar feedback and its ability to drive metal mixing within the interstellar medium (ISM) and beyond the galaxy in outflows. However, we are far from a complete understanding of feedback and galactic chemodynamics in general. 
In order to better understand the relationship between feedback and galactic chemical evolution, we have developed a new model for stellar feedback at grid resolutions of only a few parsecs in global disk simulations, using the adaptive mesh refinement hydrodynamics code \textsc{Enzo}. For the first time in galaxy scale simulations, we simulate detailed stellar feedback from individual stars including asymptotic giant branch winds, photoelectric heating, Lyman-Werner dissociating radiation, ionizing radiation tracked through an adaptive ray-tracing radiative transfer method, and core collapse and Type Ia supernovae. We furthermore follow the star-by-star chemical yields using tracer fields for 15 metal species: C, N, O, Na, Mg, Si, S, Ca, Mn, Fe, Ni, As, Sr, Y, and Ba. We include the yields ejected in massive stellar winds, but neglect the winds' energetic contribution due to computational constraints. We describe these methods in detail in this work and present the first results from 500~Myr of evolution of an isolated dwarf galaxy with properties similar to a Local Group ultrafaint dwarf galaxy. We demonstrate that our physics and feedback model is capable of producing a dwarf galaxy whose evolution is consistent with observations in both the Kennicutt-Schmidt relationship and extended Schmidt relationship. Effective feedback drives significantly metal-enriched outflows, leading to low metal retention fractions consistent with observations. Finally, we demonstrate that these simulations yield valuable information on the variation in mixing behavior of individual metal species within the multi-phase interstellar medium.
\end{abstract}

@@

\begin{figure*}
\centering
\includegraphics[width=0.475\linewidth]{all_gas_schmidt_law_evolution.png}
\includegraphics[width=0.475\linewidth]{all_gass_efficiency_evolution.png}
\caption{The Kennicutt-Schmidt law (left) and extended Schmidt law (right) relationships for our galaxy as measured every megayear, plotted as points colored by time, with dark / purple early and light / green late. See text for details of the calculation.
Recent observations from the SHIELD sample \citep{Teich2016} are plotted as black points with error bars. On the left, we also give the best fit line to galaxies from the FIGGS sample from \cite{Roychowdhury2014}, and on the right we also show the best fit line and 1 $\sigma$ errors from \cite{Shi2011}.   There is no clear correlation with time in this diagram.}
\label{fig:KS}
\end{figure*}

>>>>

\begin{abstract}
%\textbf{CHANGE: Cleaned up a few sentences. better intro + last sentence. added wind caveat. removed large H2 content mention (should I put this last one back?).}
%Galactic chemical evolution is driven through stellar feedback and its ability to drive metal mixing within the interstellar medium (ISM) and beyond the galaxy in outflows. However, we are far from a complete understanding of feedback and galactic chemodynamics in general. 
In order to better understand the relationship between feedback and galactic chemical evolution, we have developed a new model for stellar feedback at grid resolutions of only a few parsecs in global disk simulations, using the adaptive mesh refinement hydrodynamics code \textsc{Enzo}. For the first time in galaxy scale simulations, we simulate detailed stellar feedback from individual stars including asymptotic giant branch winds, photoelectric heating, Lyman-Werner dissociating radiation, ionizing radiation tracked through an adaptive ray-tracing radiative transfer method, and core collapse and Type Ia supernovae. We furthermore follow the star-by-star chemical yields using tracer fields for 15 metal species: C, N, O, Na, Mg, Si, S, Ca, Mn, Fe, Ni, As, Sr, Y, and Ba. We include the yields ejected in massive stellar winds, but greatly reduce the winds' velocities due to computational constraints. We describe these methods in detail in this work and present the first results from 500~Myr of evolution of an isolated dwarf galaxy with properties similar to a Local Group ultrafaint dwarf galaxy. We demonstrate that our physics and feedback model is capable of producing a dwarf galaxy whose evolution is consistent with observations in both the Kennicutt-Schmidt relationship and extended Schmidt relationship. Effective feedback drives significantly metal-enriched outflows, leading to low metal retention fractions consistent with observations. Finally, we demonstrate that these simulations yield valuable information on the variation in mixing behavior of individual metal species within the multi-phase interstellar medium.
\end{abstract}

@@

\begin{figure*}
\centering
\includegraphics[width=0.475\linewidth]{all_gas_schmidt_law_evolution.png}
\includegraphics[width=0.475\linewidth]{all_gass_efficiency_evolution.png}
\caption{The Kennicutt-Schmidt law (left) and extended Schmidt law (right) relationships for our galaxy as measured every megayear, plotted as points colored by time, with dark / purple early and light / green late. See text for details of the calculation. Recent observations from the SHIELD sample Teich2016 are plotted as black points with error bars. On the left, we also give the best fit line to galaxies from the FIGGS sample from Roychowdhury2014, and on the right we also show the best fit line and 1 $\sigma$ errors from Shi2011. There is no clear correlation with time in this diagram.} %something is breaking here in compiling
\label{fig:KS}
\end{figure*}
